### 2018-03-17 Sections/cryptowars.tex
Bloch sphere, dyn dec
minor
More figures

%
% Computational vs Information-Theoretic Security
%

\subsection{Computational vs information-theoretic security}\index{Computational security}\index{Information-theoretic security}\label{sec:comp_vs_inf_th_sec}

Before describing any specific cryptographic protocols, let us define what is meant by `security' in a cryptographic context.

We differentiate between \textit{information theoretic security}\index{Information-theoretic security}, as opposed to \textit{computational security}\index{Computational security}.

@@

The BB84 protocol is described in detail in Alg.~\ref{alg:bb84} in the context of polarisation-encoded photons, which is the most natural (but not only) setting for this protocol.

@@

>>>>

%
% What is Security?
%

\subsection{What is security?}\index{Computational security}\index{Information-theoretic security}\label{sec:comp_vs_inf_th_sec}

Before describing any specific cryptographic protocols, let us define what is meant by `security' in a cryptographic context. We differentiate between \textit{information theoretic security}\index{Information-theoretic security}, as opposed to \textit{computational security}\index{Computational security}.

@@

The BB84 protocol is described in detail in Alg.~\ref{alg:bb84} in the context of polarisation-encoded photons, which is the most natural (but not only) setting for this protocol. An example evolution of the protocol is illustrated in Fig.~\ref{fig:BB84_example}

@@

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{BB84_example}
\caption{Example execution of the BB84 protocol for securely sharing random bit-strings between Alice and Bob as per Alg.~\ref{alg:bb84}. At the conclusion of the protocol, some bits are discarded (X), with those remaining guaranteed to be secret between the two parties.} \label{fig:BB84_example}	
\end{figure}

### 2018-03-17 Sections/introduction.tex
Latin quotes done
More figures

\begin{itemize}
	\item Searching unstructured databases:\index{Grover's algorithm}
		\begin{itemize}
		\item Grover's algorithm \cite{bib:Grover96}.
		\item Quadratic speedup.
		\end{itemize}
	\item Satisfiability problems\footnote{A satisfiability problem is one where we search a function's input space for a solution(s) satisfying a given output constraint. The hardest such problems, like the archetypal \textsc{3-SAT}\index{3-\textsc{SAT}} problem, are \textbf{NP}-complete.}\index{\textbf{NP} \& \textbf{NP}-complete}:
		\begin{itemize}
			\item Grover's algorithm.
			\item Quadratic speedup.
			\item Includes solving \textbf{NP}-complete problems, and brute-force cracking of private encryption keys.\index{Satisfiability problems}
			\end{itemize}
	\item Optimisation problems:
		\begin{itemize}
			\item Grover's algorithm.
			\item Quadratic speedup.
			\item Many optimisation problems are \textbf{NP}-complete or can be approximated in \textbf{NP}-complete.\index{Optimisation problems}
			\end{itemize}
	\item Period finding and integer factorisation\index{Shor's algorithm}:
		\begin{itemize}
		\item Shor's algorithm \cite{bib:ShorFactor}.
		\item Exponential speedup.
		\item This compromises Rivest, Shamir \& Adleman (RSA) public-key cryptography \cite{bib:RSA}\index{RSA encryption}\index{Public-key encryption}, the most widely used cryptographic protocol on the internet today.
		\end{itemize}
	\item Simulation of quantum systems\index{Quantum simulation}:
		\begin{itemize}
			\item Lloyd's algorithm \cite{bib:lloyd1996universal}.
			\item Exponential speedup.
			\item This includes simulation of: molecular and atomic interactions in the study of quantum chemistry or nuclear physics; interactions between drug molecules and organic molecules for drug design; genetic interactions for the study of genetics and genetic medicine; nanoscale semiconductor physics for integrated circuit design; and much more.
			\end{itemize}
	\item Simulation of quantum field theories\index{Simulating quantum field theories}:
		\begin{itemize}
		 \item Jordan-Lee-Preskill algorithm \cite{bib:JLP, bib:RohdeWavelet15}
		 \item Exponential speedup.
		 \item A key area of fundamental physics research.
		 \end{itemize}
	\item Topological big-data analysis:\index{Topological big-data analysis}
		\begin{itemize}
		\item Lloyd's algorthm \cite{bib:lloyd2016quantum, USTCexperiment}.
		\item Exponential speedup.
		\item Broad applications including: social media network analysis; consumer behaviour; behavioural dynamics; neuroscience; and higher-dimensional signal and image processing.
		\end{itemize}
	\item Solving linear systems of equations:\index{Linear systems}
		\begin{itemize}
		\item \comment{To do} \cite{bib:harrow2009quantum, bib:BerryLinear}.
		\item Exponential speedup.
		\item Widespread applications in linear algebra and calculus.
		\end{itemize}
	\item Quantum machine learning:\index{Quantum machine learning}
		\begin{itemize}
		\item Lloyd's algorithm \cite{bib:lloyd2013quantum}.
		\item This includes putting an end to humanity.
		\item \textit{Ne obliviscaris}.
		\end{itemize}
\end{itemize}
An elementary technical overview of some of these archetypal algorithms is presented in Sec.~\ref{sec:quantum_algs}.

@@

\comment{Latin quote} \index{Latin}

>>>>

\begin{itemize}
	\item Searching unstructured databases:\index{Grover's algorithm}
		\begin{itemize}
		\item Grover's algorithm \cite{bib:Grover96}.
		\item Quadratic speedup.
		\end{itemize}
	\item Satisfiability problems\footnote{A satisfiability problem is one where we search a function's input space for a solution(s) satisfying a given output constraint. The hardest such problems, like the archetypal \textsc{3-SAT}\index{3-\textsc{SAT} problem} problem, are \textbf{NP}-complete.}\index{\textbf{NP} \& \textbf{NP}-complete}:
		\begin{itemize}
			\item Grover's algorithm.
			\item Quadratic speedup.
			\item Includes solving \textbf{NP}-complete problems, and brute-force cracking of private encryption keys.\index{Satisfiability problems}
			\end{itemize}
	\item Optimisation problems:
		\begin{itemize}
			\item Grover's algorithm.
			\item Quadratic speedup.
			\item Many optimisation problems are \textbf{NP}-complete or can be approximated in \textbf{NP}-complete.\index{Optimisation problems}
			\end{itemize}
	\item Period finding and integer factorisation\index{Shor's algorithm}:
		\begin{itemize}
		\item Shor's algorithm \cite{bib:ShorFactor}.
		\item Exponential speedup.
		\item This compromises Rivest, Shamir \& Adleman (RSA) public-key cryptography \cite{bib:RSA}\index{RSA encryption}\index{Public-key encryption}, the most widely used cryptographic protocol on the internet today.
		\end{itemize}
	\item Simulation of quantum systems\index{Quantum simulation}:
		\begin{itemize}
			\item Lloyd's algorithm \cite{bib:lloyd1996universal}.
			\item Exponential speedup.
			\item This includes simulation of: molecular and atomic interactions in the study of quantum chemistry or nuclear physics; interactions between drug molecules and organic molecules for drug design; genetic interactions for the study of genetics and genetic medicine; nanoscale semiconductor physics for integrated circuit design; and much more.
			\end{itemize}
	\item Simulation of quantum field theories\index{Simulating quantum field theories}:
		\begin{itemize}
		 \item Jordan-Lee-Preskill algorithm \cite{bib:JLP, bib:RohdeWavelet15}
		 \item Exponential speedup.
		 \item A key area of fundamental physics research.
		 \end{itemize}
	\item Topological big-data analysis:\index{Topological big-data analysis}
		\begin{itemize}
		\item Lloyd's algorthm \cite{bib:lloyd2016quantum, USTCexperiment}.
		\item Exponential speedup.
		\item Broad applications including: social media network analysis; consumer behaviour; behavioural dynamics; neuroscience; and higher-dimensional signal and image processing.
		\end{itemize}
	\item Solving linear systems of equations:\index{Linear systems}
		\begin{itemize}
		\item \comment{To do} \cite{bib:harrow2009quantum, bib:BerryLinear}.
		\item Exponential speedup.
		\item Widespread applications in linear algebra and calculus.
		\end{itemize}
	\item Quantum machine learning:\index{Quantum machine learning}
		\begin{itemize}
		\item Lloyd's algorithm \cite{bib:lloyd2013quantum}.
		\item This includes putting an end to humanity.
		\item \textit{Ne obliviscaris}.
		\end{itemize}
\end{itemize}
An elementary technical overview of some of these archetypal algorithms is presented in Sec.~\ref{sec:quantum_algs}.

@@

### 2018-03-17 Sections/optical_encoding_of_quantum_information.tex
More figures

We can encode a single qubit into a single photon in the polarisation basis using the horizontal and vertical polarisation degrees of freedom. Equivalently, one can employ `dual rail' encoding, whereby a single photon is placed into a superposition across two spatial modes. Finally, one can use time-bin encoding, whereby discrete windows of time represent logical basis states when occupied by a photon. This leads to the equivalent representations for logical qubits ($L$),
\begin{align} \label{eq:single_photon_enc}\index{Polarisation encoding} \index{Dual-rail encoding}
\ket{\psi}_\text{qubit} &\equiv \alpha\ket{0}_L + \beta\ket{1}_L, \nonumber \\
\ket{\psi}_\text{pol} &\equiv \alpha\ket{H} + \beta\ket{V}, \nonumber \\
\ket{\psi}_\text{dual} &\equiv \alpha\ket{0,1} + \beta\ket{1,0}, \nonumber \\
\ket{\psi}_\text{temporal} &\equiv \alpha\ket{0_t,1_{t+\tau}} + \beta\ket{1_t,0_{t+\tau}}.
\end{align}
Conversion between polarisation and dual-rail encoding is straightforward and deterministic using standard optical components, as described in Fig.~\ref{fig:pol_to_dual_conv}.

>>>>

We can encode a single qubit into a single photon in the polarisation basis using the horizontal and vertical polarisation degrees of freedom. Equivalently, one can employ `dual rail' encoding, whereby a single photon is placed into a superposition across two spatial modes. Finally, one can use time-bin encoding, whereby discrete windows of time represent logical basis states when occupied by a photon. This leads to the equivalent representations for logical qubits ($L$),
\begin{align} \label{eq:single_photon_enc}\index{Polarisation encoding} \index{Dual-rail encoding}
\ket{\psi}_\text{qubit} &\equiv \alpha\ket{0}_L + \beta\ket{1}_L, \nonumber \\
\ket{\psi}_\text{pol} &\equiv \alpha\ket{H} + \beta\ket{V}, \nonumber \\
\ket{\psi}_\text{dual} &\equiv \alpha\ket{0,1} + \beta\ket{1,0}, \nonumber \\
\ket{\psi}_\text{temporal} &\equiv \alpha\ket{0_t,1_{t+\tau}} + \beta\ket{1_t,0_{t+\tau}},
\end{align}
shown graphically in Fig.~\ref{fig:photonic_qubit_encodings}.

\begin{figure}[!htb]
\includegraphics[width=0.2\textwidth]{photonic_qubit_encodings}
\caption{Three approaches to encoding a single qubit using a single photon, via a superposition across two spatial ($A$ and $B$), polarisation ($V$ and $H$) or temporal ($t$ and \mbox{$t+\tau$}) modes.} \label{fig:photonic_qubit_encodings}
\end{figure}

Conversion between polarisation and dual-rail encoding is straightforward and deterministic using standard optical components, as described in Fig.~\ref{fig:pol_to_dual_conv}.

### 2018-03-17 Sections/quantum_algorithms.tex
More figures

Such \textbf{NP}-complete algorithms can be quadratically enhanced in runtime using Grover's algorithm. To see this, note that all \textbf{NP}-complete problems can be efficiently mapped to one another with polynomial resource overhead (see Fig.~\ref{fig:complexity_classes}). Thus, we can restrict ourselves to considering the satisfiability problems\index{Satisfiability problems} discussed above -- the archetypal \textbf{NP}-complete problems.

@@

\comment{Boson-sampling and IQP. Other sampling problems.}

>>>>

Such \textbf{NP}-complete algorithms can be quadratically enhanced in runtime using Grover's algorithm. To see this, note that all \textbf{NP}-complete problems can be efficiently mapped to one another with polynomial resource overhead (see Fig.~\ref{fig:complexity_classes}). Thus, we can restrict ourselves to considering the satisfiability problems\index{Satisfiability problems} discussed above -- the archetypal \textbf{NP}-complete problems. An example of the {\sc 3-SAT} problem\index{3-\textsc{SAT} problem }, which is \textbf{NP}-complete, is shown in Fig.~\ref{fig:3SAT}.

\begin{figure}[!htb]
\includegraphics[width=0.3\textwidth]{3SAT}
\caption{Digital circuit for an instance of the {\sc 3-SAT} problem. Each or the OR gates is input with some combination of the input bits or their compliments (i.e with a NOT gate). Each of these is referred to as a `clause', of which there are 4 in this example, but could be any number in general. The final AND gate requires that all clauses be simultaneously satisfied in order to yield a final output of `1'. The goal of the problem is to find an input bit-string that yields an output of `1'. In general, this may require exhaustively searching over the entire space of input states via brute-force, which exhibits time-complexity exponential in the length of the bit-string. This problem is proven to be \textbf{NP}-complete.} \label{fig:3SAT}	
\end{figure}

@@

\index{Galton board}
\index{Sampling problems}

Sec.~\ref{sec:BS}
\comment{Boson-sampling and IQP. Other sampling problems.}

\begin{figure}[!htb]
\includegraphics[width=0.4\textwidth]{galton_board}
\caption{The Galton board yields a very simple classical sampling problem. Balls (red) are input at the top and allowed to fall freely through the pyramid network of pegs (grey), at which balls bounce to the left or right with 50\% probability. At the output the balls are collected into buckets, which populate according to a binomial distribution\index{Binomial distribution}. The computational problem is to produce statistically accurate samples from such a device, which classically is efficiently implemented by sampling the binomial distribution.}	\label{fig:galton_board}\index{Galton board}
\end{figure}
